Results

### 2018-03-15 02_analysis.Rmd
Add explanation of which coefficients to add

# Interpreting models

This is like using ANOVA, but more complex and flexible. Coefficients represent changes from the baseline intercept value.

>>>>

# Interpreting interactions in models

Ordinarily, people use ANOVA to analyze 3-way, 2 × 2 × 2 factorial designs, [like this](https://mypages.valdosta.edu/mwhatley/3600/2x2x2.htm). A more flexible ([yet identical!](https://www.theanalysisfactor.com/why-anova-and-linear-regression-are-the-same-analysis/)) way to do this is to use a regular regression model with interaction terms for each of the conditions, like so (here we use three, since we can use simper models to get averages for the larger umbrella groups, like just crackdowns and crackdown + issue):

- Model 1:

    $$
    y = \beta_0 + \beta_1 \text{Crackdown}
    $$

- Model 2:

    $$
    \begin{aligned}
    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue } + \\
    & \beta_3 \text{Crackdown} \times \text{Issue}
    \end{aligned}
    $$

- Model 3:

    $$
    \begin{aligned}
    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue} + \beta_3 \text{Funding } + \\
    & \beta_4 \text{Crackdown} \times \text{Issue } + \\
    & \beta_5 \text{Crackdown} \times \text{Funding } + \\
    & \beta_6 \text{Issue} \times \text{Funding } + \\
    & \beta_7 \text{Crackdown} \times \text{Issue} \times \text{Funding}
    \end{aligned}
    $$

Adding different combinations of the coefficients provides the average values for each combination of factors, which corresponds to the average likelihood and amount donated table above.

```{r interaction-interpretation, results="asis"}
model1 <- "1"
model2 <- "2"
model3 <- "3"

interpretation <- tribble(
  ~Model, ~`Coefficients to add together`,
  model3, "Intercept",
  model3, "Intercept + Funding",
  model2, "Intercept",
  model3, "Intercept + Issue",
  model3, "Intercept + Issue + Funding + (Issue × Funding)",
  model2, "Intercept + Issue",
  model1, "Intercept",
  model3, "Intercept + Crackdown",
  model3, "Intercept + Crackdown + Funding + (Crackdown × Funding)",
  model2, "Intercept + Crackdown",
  model3, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
  model3, "Intercept + Crackdown + Issue + Funding + (Crackdown × Issue) + (Crackdown × Funding) + (Issue × Funding) + (Crackdown × Issue × Funding)",
  model2, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
  model1, "Intercept + Crackdown"
)

conditions_summary_clean %>% 
  select(1:3) %>% 
  slice(-n()) %>% 
  bind_cols(interpretation) %>% 
  pandoc.table()
```
